---
title: "Health Catalyst Intro R"
author: "Michael Levy"
date: "April 10, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

# Setup and notes

MCQ: http://tinyurl.com/catalyst-mcq  
Live-script: http://tinyurl.com/catalyst-script  

# Intro R & RStudio

- Why R?
    - First: Why code?
        - Power
        - Flexibility
        - Editability -- error fixing, tweaks
        - Traceability -- return and know what was done
        - Reproducability
        - Communication -- no ambiguity
    - Built for data analysis
    - Extended
    - User community
    - Full-fledged programming language
        - **Run hello world** 
- Why RStudio?
    - **Open it**
    - Integrates and organizes: 3 panels
    - Cross-platform (incl. AWS)

Console vs. script

- **Introduce live_script**
- Pushing code & keyboard shortcuts

## R Basics

- Calculator
    - Hanging command  
    - Order of operations
- Whitespace
- Comments
- Scientific notation
- Functions - `log`
    - Nested functions - `log(exp(2))`
- Comparison
- Variable assignment, reassignment
    - **MCQ #1**
- variable_name_conventions
    - tab auto-complete
    
## Digging in

- help
    - ?log
    - ??logarithm
    - google / SO
    - Cookbook
    - RStudio cheatsheets
- Arguments to functions -- `log`
    - **MCQ #2**
- Errors, warnings, and messages
- **Data challenge**


# Projects

- Idea of a script that does everything
    - Keep raw data sacrosanct
    - Output is disposable
- Good organization makes life easier
    - **Show viticulture dir**
- RStudio projects help
    - Walk through an example
    - **Project setup exercise**
    
    
# Data frames

- Create a new script
- `library(tidyverse)`
- read_csv the data
    - library and read_csv are functions
    - have to assign `read_csv()` to variable
- Examine & explain dataset
    - Rows and columns. 
    - Click in Environment to see spreadsheet
- **Shoutout: `summary`**
    - Oldest person in the dataset?

# Visualization

- Why visualization in hour 1
- ggplot part of tidyverse, base and lattice
- Three pieces: data, coordinate system, layers

```{r}
ggplot(d, aes(x = age, y = days_to_appt)) + 
    geom_point()
```

- Just ggplot call
    - Assign and build
    - Can add details, e.g.axis labels
- **Challenge: risk vs age**

## Continuous vs. discrete variables

#### One continuous variable: density curve or histogram

```{r}
ggplot(d, aes(x = age)) + 
    geom_density()

ggplot(d, aes(x = age)) + 
    geom_histogram()
```

- Set color and fill manually

#### One discrete variable: bar

```{r}
ggplot(d, aes(x = reminders)) +
    geom_bar(stat = "count")
```

#### One discrete, one continuous

```{r}
ggplot(d, aes(x = status, y = age)) + 
    geom_boxplot()

ggplot(d, aes(fill = status, x = age)) + 
    geom_density(alpha = .5)
```

- Or, density curves with diff fill
    - Set alpha
    - Change theme

- **Challenge: boxplots**   
    - Log y

```{r}
ggplot(d, aes(y = days_to_appt, color = status, x = subsidized)) + 
    geom_boxplot() +
    scale_y_log10()
```


#### Two discrete variables (bar)
    - Position: stack, dodge, fill
    
```{r}
ggplot(d, aes(x = gender, fill = status)) +
    geom_bar(stat = "count", position = "dodge")
```

#### Two continuous, one discrete?

- Earlier bonus: risk vs. age by subsidized
- Overplotting: Smaller/alpha points
    - Demo aes vs. hard-setting
- Smoothers
    - lm vs. loess
- aes to all vs. some layers
    - size, linetype
    
```{r}
ggplot(d, aes(x = age, y = days_to_appt, color = subsidized)) + 
    geom_point() + 
    geom_smooth(method = "lm")
```

**MCQ: Which plot?**



## Faceting

```{r}
ggplot(d, aes(x = health_risk, fill = status)) + 
    geom_density(alpha = .5) +
    facet_wrap(~ gender)
    
ggplot(d, aes(x = health_risk, fill = status)) + 
    geom_density(alpha = .5) +
    facet_grid(gender ~ subsidized, labeller = label_both) +
    scale_fill_brewer(palette = "Accent")
```

- Change palette
- `ggsave`

**Final exercise**

```{r}
ggplot(d, aes(x = age, y = health_risk, color = gender)) + 
    geom_point() + 
    geom_smooth(method = "lm") + 
    facet_wrap(~ subsidized) 
```
