---
title: "R Foundations"
author: "Michael Levy"
date: "July 12, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```


MCQ: http://tinyurl.com/hc-rfound-mcq  
Live script: http://tinyurl.com/hc-rfound  
Feedback: http://tinyurl.com/hc-rfound-feedback

- Today is going to be boring. Sorry.  
- Going to be a few intermediate concepts thrown in. Don't worry.  
    - Bonus questions are meant for folks with experience in R. Don't worry.  
- Invite Qs. I'll head them off if they're too advanced or whatever.

### Why R?

**Slide: Why R?**

### RStudio

- Panes
- Make script
- Options -> Pane layout
- Calculator: 
    - console
    - ctrl-enter
          - highlighting
          - current line
    - ctrl-shift-enter for whole script. End goal!
- Save script (plain text)

### Variables and assignment

- printing vs. assigning
    - `(x <- 2)`
- assign -> environment
- usefulness vs. hard-coding
- reassignment

**MCQ: Assignment**  

- On return show function creation for truffle price

### Data types

Three basic types:

1. Logical
1. Numeric (integers, doubles, etc.)
1. Character  
    - Unquoted variables, quoted strings

Logical comparison

Data containers:

**Slide: data structures**

### Functions & Arguments

```{r}
c(2, 4, 6, 8)
sum(2, 4, 6, 8)
evens <- c(2, 4, 6, 8)
evens
sum(evens)
sqrt(evens) 
```

Just saw two types of vectorized functions

Can also vectorize over multiple vectors:

```{r}
odds = c(1, 3, 5, 7)
evens + odds
evens - odds
```

#### Vector comparisons

```{r}
evens > odds
evens == 4  # recycling
```

Other ways to create vector:

```{r}
1:100
letters; LETTERS
```

Vectorization makes R fast. `mean(1:1e8)`



### Multiple arguments

*Don't do help here*

```{r}
rep(3, 4)
rep("abc", 5)
```

### Named arguments and Getting help

```{r}
rnorm(10, 100, 10)
rnorm(n = 10, mean = 100, sd = 10)
rnorm(10)  # Shout-out: What are mean and sd and how did R know?
```

- `?rnorm`  
- Show rbinom, pbinom, qbinom for fun

**Slide: Finding and using functions**

### Subsetting

By index

```{r}
threes[1]
threes[1:3]
letters[10]
LETTERS[c(8, 3)]
```

By logical

```{r}
threes[threes == 9]  # Common idiom
threes[threes > 50]
threes[threes > 50 & threes < 90]
threes[threes < 10 | threes == 90]
threes[sqrt(threes) %% 1 == 0]
```

**Slide: Subsetting**

- Show replicate on return

### Missing values

- `NA` is missing. `NULL` is different

```{r}
withMissing = threes[c(1, 10, 50)]
sum(withMissing)
sum(withMissing, na.rm = TRUE)
is.na(withMissing)
withMissing[is.na(withMissing)] <- 0
```


### Data frames

```{r}
df = data.frame(letters = c("a", "b", "c"), numbers = c(1, 2, 3))
df
df$numbers
df$numbers^2
df$squares = df$numbers^2
df
```

Let's get real

Mention `DBI::dbConnect`

```{r}
readmit <- read.csv("https://www.dropbox.com/s/2njq3fbt6v541xq/diabetes_readmit.csv?dl=1")
head(readmit)
str(readmit)
summary(readmit)
View(readmit)
```

```{r}
readmit$age
sort(readmit$age)
table(readmit$gender)
table(readmit$gender, readmit$race)

sort(readmit$age[readmit$medical_specialty == "Cardiology"])
mean(readmit$age[readmit$medical_specialty == "Cardiology"], na.rm = TRUE)
mean(readmit$age[readmit$medical_specialty != "Cardiology"], na.rm = TRUE)
# How would we decide if that difference is meaningful?

# tmp column first, then overwrite
readmit$readmitted <- ifelse(readmit$readmitted == "NO", "No", "Yes")  # do I need the ifelse?
```

**Slide: Putting it all together**


### Packages

A random package to show some power.

```{r, eval = TRUE}
# install.packages("leaflet")
library("leaflet")
leaflet() %>%
  addTiles() %>%
  # addProviderTiles("OpenTopoMap") %>%
  addMarkers(lat = 40.632991, lng = -111.803945, label = "Us!")
```

More on Leaflet: http://rstudio.github.io/leaflet/  
Some top R packages: https://support.rstudio.com/hc/en-us/articles/201057987-Quick-list-of-useful-R-packages  
Much more on R packages: https://cran.r-project.org/web/views/

### Working with text

If time allows. 

There's an easy exercise in slides.
